{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-03 bmvc_review.tex
revision.

{\it Burak: What we wrote here didn't match what you told me. Go over
  the following paragraph and change the numbers correctly.}

The order of running these three KCFs is important because each of
these filters aims at addressing different challenges; The
\textit{target+large background} translation filter, $R_{t}^{L}$, is
applied to the $i$th and $i+1$th image frame, another translation filter,
$R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image frame, and then the scale
filter, $R_{s}$ is applied to the $i+4$the image. This order repeats
until the end of the image frames. The translation filter,
$R_{t}^{L}$, is intended to run right after the scale filter, $R_s$,
runs which is applied at every other $i+2$ frames. We run these two
filters this way because we want to minimize any drifts that are
likely to happen running only $R_{s}$. In addition, the filter,
$R_{t}^{S}$, is applied to every other frames before $R_{s}$ and right
after two consecutive frames running $R_{t}^{L}$. By iterating this
order of learning KCFs, we can integrate more discriminative shape
features that can not be fully learned by $R_{t}^{L}$ as it contains
contribution of large background in the learned model. The filter,
$R_{t}^{L}$, uses shape and color information together to recover from
any potential drifts -- drifts could happen only looking the target's
scale by the filter, $R_{s}$.

>>>>

The order of running these three KCFs is important because each of
these filters aims at addressing different challenges; The
\textit{target+large background} translation filter, $R_{t}^{L}$, is
applied to the $i$th and $i+1$th image frame, another translation
filter, $R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image frame,
and then the scale filter, $R_{s}$ is applied to the $i+4$the
image. This order repeats until the end of the image frames. The
translation filter, $R_{t}^{L}$, is intended to run right after the
scale filter, $R_s$, runs which is applied at every other $i+4$
frames. We run these filters in this way because we want to minimize
any drifts that are likely to happen running only $R_{s}$. In
addition, the filter, $R_{t}^{S}$, is applied to every other two
frames before $R_{s}$ and right after two consecutive frames running
$R_{t}^{L}$. By repeating this order of learning KCFs, we can
integrate more discriminative shape features that cannot be learned by
$R_{t}^{L}$ because it incorporates a large area about background in
the learned model. The filter, $R_{t}^{L}$, uses shape and color
information together to recover from any potential drifts -- drifts
could happen only looking the target's scale by the filter, $R_{s}$.
